### 2016-11-07 Manuscript/SW_early_life_telomeres.Rmd
Home eds

Longitudinal data showed that early-life RTL was not related to adult RTL (R^2^ = `r round2(summary(lm(RTL1~RTL+TimeDiff,data = dd3))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data = dd3))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = dd3))$coefficients[2,4])`; Fig. 4A). Running this analysis separately for juvenile age classes revealed that this relationship was not significant for nestlings (R^2^ = `r round2(summary(lm(RTL1~RTL,data=subset(dd3,Agemonths == 1)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL,data=subset(dd3,Agemonths == 1)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL,data = subset(dd3,Agemonths == 1)))$coefficients[2,4])`), fledglings (R^2^ = `r round2(summary(lm(RTL1~RTL,data=subset(dd3,Agemonths == 6)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL,data=subset(dd3,Agemonths == 6)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL,data = subset(dd3,Agemonths == 6)))$coefficients[2,4])`) or subadults (R^2^ = `r round2(summary(lm(RTL1~RTL,data=subset(dd3,Agemonths == 10)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL,data=subset(dd3,Agemonths == 10)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL,data = subset(dd3,Agemonths == 10)))$coefficients[2,4])`). $\Delta$RTL was significantly lower than zero in nestlings (t = `r round2(t.test(subset(dd3,Agemonths == 1)$DeltaRTL)$statistic)`; P `r round3(t.test(subset(dd3,Agemonths == 1)$DeltaRTL)$p.value)`), but not in fledglings (t = `r round2(t.test(subset(dd3,Agemonths == 6)$DeltaRTL)$statistic)`; P = `r round2(t.test(subset(dd3,Agemonths == 6)$DeltaRTL)$p.value)`) or subadults (t = `r round2(t.test(subset(dd3,Agemonths == 10)$DeltaRTL)$statistic)`; P = `r round2(t.test(subset(dd3,Agemonths == 10)$DeltaRTL)$p.value)`), suggesting that telomere shortening was highest shortly after the nestling phase, after which both telomere shortening and telomere lengthening were observed (Fig. 4B).

>>>>

Longitudinal data showed that early-life RTL was weakly, but significantly, related to adult RTL (R^2^ = `r round3(summary(lm(RTL1~RTL,data = dd3))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL,data = dd3))$coefficients[2,3])`; P = `r round3(summary(lm(RTL1~RTL,data = dd3))$coefficients[2,4])`; Fig. 4A). $\Delta$RTL was significantly lower than zero in nestlings (t = `r round2(t.test(subset(dd3,Agemonths == 1)$DeltaRTL)$statistic)`; P `r round3(t.test(subset(dd3,Agemonths == 1)$DeltaRTL)$p.value)`), but not in fledglings (t = `r round2(t.test(subset(dd3,Agemonths == 6)$DeltaRTL)$statistic)`; P = `r round2(t.test(subset(dd3,Agemonths == 6)$DeltaRTL)$p.value)`) or subadults (t = `r round2(t.test(subset(dd3,Agemonths == 10)$DeltaRTL)$statistic)`; P = `r round2(t.test(subset(dd3,Agemonths == 10)$DeltaRTL)$p.value)`), suggesting that telomere shortening was highest shortly after the nestling phase, after which both telomere shortening and telomere lengthening were observed (Fig. 4B).

### 2016-11-07 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Home eds

x <- subset(subset(dd,Ageclass 'A'))

summary(lm(RTL~Tarsus,data = x))

dd$Sex2 <- paste(dd$Fledged,dd$Sex)

ggplot(dd,aes(x = Tarsus, y = RTL,col = Sex2))+
geom_smooth(method = 'lm')

>>>>

temp <- dd14

Fig4A <- ggplot(temp,
       aes(x = Agemonths,
           col = factor(SurvivedNext),
           y = RTL)) +
  ylab('RTL') + 
  xlab('Survival probability') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none') +
  geom_smooth(method = 'lm')
  annotate('text',x = 17,y = 2.5,label = 'C')

temp <- ddply(juv14,
              .(LayYear,Fledged),
              summarise,
              MeanTL = median(RTL),
              Survived = mean(SurvivedNext),
              n = length(RTL)) %>%
  subset(n > 9)

ggplot(temp,aes(x = MeanTL,y = Survived,col = Fledged))+
  geom_point()+
  stat_smooth(method = 'lm')

Fig4B <- ??

pdf('Figures/Figure 4.pdf',
    width = 8,
    height = 8,
    paper = 'a4')
multiplot(Fig4A,Fig4B,layout = matrix(c(1,2),nrow = 2,byrow = T))
dev.off()
